Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic

### 2018-04-09 docs/Manuscript.Rmd
Modified methods section

@@

Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$. Since $b = m$, we will only use $b$ throughout the paper for simplicity. The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}. Both coefficients were tested against the null hypothesis of no change (*i.e.* $H_0: c = 0$ and $H_0: b = 0$). Additionally, the allometric parameter was tested against the null hypothesis of isometric growth ($H_0: b = 3$). Coefficients were tested with a two-tailed Student's t-test. The significance of the regression was corroborated with an F-test.

@@

Since uncertainty around estimated relationships was not reported in some of the reviewed studies, it was not possible to test for statistical differences between relationships. Instead, the 16 length-weight relationships were used to calculate expected weight length observations of the organisms sampled from the Central Mexican Caribbean (n = 109). Expected weights were divided by the observed weights to obtain a ratio. Difference in mean weight ratios across studies were tested with a one-way Analysis of Variance (ANOVA).

All hypothesis testing was performed with an *a priori* confidence level of $\alpha = 0.01$ in R version 3.4.0 \citep{rcore_2017}. Raw data and code used in this work is available at dryad.org.

@@

robust_se <- TidyModel$std.error %>%
  set_names(TidyModel$term)

wald_results <- waldtest(model, vcov = vcovHC(model, type = "HC1"))

f_string <- c("F Statistic", paste0(formatC(wald_results$F[2], digits = 2, format = "f"), "*** (df = 1; ", dim(fish)[1]-2,")"))

@@

a <- coefficients(model)[[1]]
b <- coefficients(model)[[2]]

predicted_this_study <- data.frame(Length = seq(min(fish$Length), max(fish$Length), by = 1)) %>% 
  mutate(Weight = 10^a*Length^b)
```

>>>>

Parameters from the central Mexican Caribbean were obtained from data collected in `r length(unique(fish$Location))` sampling sites along the Central Mexican Caribbean coast in 2010 (Table S1). Sampling locations included wall and carpet reefs at depths between `r min(fish$Depth_m)` m and `r max(fish$Depth_m)` m.  All observed lionfish (n = `r dim(fish)[1]`) were collected using hand nets and numbered collection bottles. The use of hand nets prevented any weight loss due to bleeding and allowed a better representation of small sizes by eliminating gear selectivity. Organisms were euthanized (via pithing) and Total Length (TL; mm) and Total Weight (TW; gr) were recorded before freezing organisms.

@@

Where $Y = log_{10}(TW)$, $X = log_{10}(TL)$, $m = b$, and $c = log_{10}(a)$. Since $b = m$, we will only use $b$ throughout the paper for simplicity. The coefficients ($c$ and $b$) were estimated with  an Ordinary Least Square Regression and heteroskedastic-robust standard error correction \citep{zeileis_2004}. Both coefficients were tested against the null hypothesis of no change (*i.e.* $H_0: c = 0$ and $H_0: b = 0$) and the null hypothesis of isometric growth ($H_0: b = 3$). Coefficients were tested with a two-tailed Student's t-test. The significance of the regression was corroborated with an F-test.

@@

Since uncertainty around estimated relationships was not reported in some of the reviewed studies, it was not possible to test for statistical differences between relationships. Instead, the 16 length-weight relationships were used to calculate predicted weight from length observations of the organisms sampled from the Central Mexican Caribbean. Predicted weights were divided by the observed weights to obtain a ratio. Difference in mean weight ratios across studies were tested with a one-way Analysis of Variance (ANOVA). All analyses were performed in R version 3.4.4 \citep{rcore_2018}. Raw data and code used in this work is available at dryad.org.

@@

robust_se <- TidyModel$std.error %>%
  set_names(TidyModel$term)
```

@@

a <- coefficients(model)[[1]]
b <- coefficients(model)[[2]]
```
